\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Deepak Prakash} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 7463092901 \\ Gaya, Bihar} 
\address{\href{mailto:kumardeepakbabu@gmail.com}{kumardeepakbabu@gmail.com} \\ \href{https://github.com/7dpk}{github.com/7dpk}} %
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{ABOUT}
{DevOps and Machine Learning enthusiast with 6+ months of experience in building Deep Learning models, 4+ months experience in Blockchain development(hyperledger, solidity) and 2+ years of experience in Backend and DevOps.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science} 8.4 CGPA BCE, Bhagalpur \hfill {Expected 2023}\\
Relevant Field of Study: ML, Deep Learning, Micro-services and DevOps.

{\bf Sr. Secondary(12th CBSE)} 77.2\%, SST Tilaiya \hfill {2016 - 2018}

{\bf High School(10th CBSE)} 93.5\%, SST Tilaiya \hfill {2011 - 2016}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & TypeScript, Python, C++, Solidity
\\
Frameworks/Skills & AWS, DevOps, Deep Learning, Blockchain, GraphQL, Kubernetes\\
Languages & Hindi, English, French\\
Certifications & 
{\href{https://coursera.org/share/a784f996ac079781368a80690a3480ba}{ML Specialization},{\href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS35S4321042602113804}{ Deep Learning},
\href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS44S1321024002113804}{Blockchain},
\href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS83S3463013210183832}{Deep Learning using HPC},
\href{https://coursera.org/verify/KUYSGKXZ2VGK}{Cloud 101},
\\
   & \href{https://coursera.org/share/78c3907a0a1a98b932e43ae0d23dcd8f}{Statistics with SAS}

\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}
 
\textbf{Full Stack Developer,Co-founder} \hfill Jul 2020 - Mar 2021\\
Vidyayan Eduventures Pvt. Ltd.(Funded by Government of Bihar) \hfill \textit{Bhagalpur, Bihar}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved 1K+ User Base for Vidyayan  using Optimized site and simple user interface.
     \item Led the technical team to Develop our own Virtual Meet platform(vidyayan meet).
    \item Developed Backend that did Login/Register(Oauth), Dashboard, Distance Matrix using NodeJS, AWS, and Google Map API. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{\href{https://github.com/7dpk/pytorch-simple-chatbot}{Deep Learning Chat bot}} {Built a neural network based chat bot using pytorch and NLTK for natural language processing. The chat bot can handle automatic orders and billing from the customers. The model is trained using small dataset but can be extended using users own personal database.}
\item \textbf{\href{https://github.com/7dpk/k8s-express-node-redis-postgres}{Microservice Based Website}} {Built a Microservice based web-app leveraging NodeJS, Kubernetes, Postgresql, Redis and express. The app was deployed on AWS EKS platform which empowered it seamless scaling and fast operation using redis and containers to isolate the workflow }
\item \textbf{\href{https://github.com/kapeed7/chess_bot}{OpenCV Chess Bot}} { Built a Computer Vision based bot in python, to enable chess playing on any screen without any intervention, leveraged sockets/threading connected to cloud server for more power full computation using Stockfish and handling multiple client at once. }
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Avid reader, loves playing Basketball, Volleyball and Table Tennis
    \item	Loves playing chess, sketching and playing guitar.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Technical Lead at Vidyayan Eduventures with over 1k+ users
    \item Coordinator Debugerzz Coding Club (BCE Bhagalpur) with over 150+ members.
\end{itemize}


\end{rSection}


\end{document}
