\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Deepak Prakash} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 7463092901 \\ Gaya, Bihar} 
\address{\href{mailto:kumardeepakbabu@gmail.com}{deepakprakashx@gmail.com} \\ \href{https://github.com/7dpk}{github.com/7dpk} \\ \href{https://dp7.me}{dp7.me} \\ \href{https://www.linkedin.com/in/dpk7/}{LinkedIn}}%
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{ABOUT}
{A Backend Developer with a passion for DevOps and Machine Learning. Experienced in building microservices and Deep Learning models, I also bring a keen interest in Blockchain and Cyber Security.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science} 8.4 CGPA BCE, Bhagalpur \hfill {Expected 2023}

{\bf Sr. Secondary(12th CBSE)} 87.2\%, SST Tilaiya \hfill {2016 - 2018}

{\bf High School(10th CBSE)} 93.5\%, SST Tilaiya \hfill {2011 - 2016}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, TypeScript, C++, Solidity, bash, Golang
\\
Frameworks/Skills & MERN, SQL, MongoDB, AWS, GCP, Django, web3js, tensorflow, Kubernetes\\
Languages & Hindi, English, French\\
Certifications & 
\href{https://learn.mongodb.com/c/zJuDb8CJQNae4-pBO-WEcQ}{MongoDB Associate Developer}, 
\href{https://coursera.org/share/a784f996ac079781368a80690a3480ba}{ ML Specialization}, 
\href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS35S4321042602113804}{ Deep Learning},



\\
   & 
   \href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS44S1321024002113804}{ Blockchain Applications},\href{https://nptel.ac.in/noc/E_Certificate/NPTEL22CS83S3463013210183832}{ Deep Learning using HPC},\href{https://coursera.org/share/78c3907a0a1a98b932e43ae0d23dcd8f}{ Statistics with SAS}

\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Back-end Developer} \hfill Dec 2022 - Mar 2023\\
SOLVE CHAMP \hfill \textit{Patna, Bihar}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Successfully grew user base to over a thousand.
     \item Single-handedly developed a vector DB powered solution that recommends questions to the test-takers.
    \itemI I developed a GraphQL backend using TypeScript and a code-first approach, implementing microservices for authentication and dashboard functionality. 
 \end{itemize}
 
\textbf{Full Stack Developer, Co-founder} \hfill Jul 2020 - Mar 2021\\
Vidyayan Eduventures Pvt. Ltd.(Funded by Government of Bihar) \hfill \textit{Bhagalpur, Bihar}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Successfully expanded the user base to over two thousand users.
     \item Led the development of Vidyayan Meet, our proprietary virtual meeting platform.
    \item I developed the backend, dashboard, and Distance Matrix API for locating the nearest available tutor or student, incorporating smart caching for improved performance. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{\href{https://github.com/7dpk/OpenCV-Chess-Bot}{OpenCV Chess Bot: OpenCV, d3dshot, tkinter}} { Developed a Python-based Computer Vision bot for seamless chess playing on any screen. Implemented sockets and threading, leveraging cloud servers for more powerful computations with Stockfish.}
\item \textbf{\href{https://github.com/7dpk/pytorch-simple-chatbot}{PyTorch Chatbot}} {Developed a PyTorch-based chatbot with natural language processing capabilities using NLTK. Automated customer orders and billing. Trained on a small dataset but easily extensible with user data.}
\item \textbf{\href{https://github.com/7dpk/k8s-express-node-redis-postgres}{Scalable web app: NodeJS, Kubernetes, and microservices.}} {Developed a scalable web app using NodeJS, Kubernetes, Postgresql, Redis and Express, implemented as a Microservice architecture. The app was deployed on AWS EKS platform, allowing for effortless scaling and efficient workflow isolation with containers and Redis. }
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
    \begin{itemize}
    \item 	Avid reader, loves playing Basketball, Volleyball and Table Tennis
    \item	Loves playing chess, sketching and playing guitar.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------



\end{document}
